The Galaxy Cluster Merger Catalog: An Online Repository of Mock Observations from Simulated Galaxy Cluster Mergers

### 2016-09-12 paper/ms.tex
Shorten yt hub section a bit

\subsubsection{The yt Hub}\label{sec:yt_hub}
The yt Hub~(\textbf{citeme}) is a conglomerate of various open source services
creating an environment that allows to collect, remotely analyze, share and
publish scientific datasets. At its core yt Hub uses Girder~(\textbf{citeme}) --
a data management platform that allows to transparently store, serve, and proxy
data from heterogeneous backend storage engines through a single RESTful web
API, including local filesystems, MongoDB databases, Amazon S3-compliant
key-value stores, and Hadoop Distributed Filesystems (HDFS). Data served by
Girder can be easily gathered into dynamical hierarchies such as collections,
folders and items. This data management system is integrated with
JupyterHub~(\textbf{citeme}) and allows authenticated users to spawn Jupyter
notebook servers with the direct access to data that is provided as a
dynamically composed FUSE filesystem. Any Jupyter notebook created in that
environment during an interactive session is safely stored back in the Girder
instance, preserving the user's analysis workflow and increasing research
reproducibility.

>>>>

\subsubsection{The yt Hub}\label{sec:yt_hub}
The catalog data is stored on the yt Hub~(\textbf{citeme}), a conglomerate of various open source services creating an environment that allows to collect, remotely analyze, share and publish scientific datasets. At its core yt Hub uses Girder~(\textbf{citeme}), a data management platform that allows to transparently store, serve, and proxy data from heterogeneous backend storage engines through a single web API. Data served by Girder can be easily gathered into dynamical hierarchies such as collections, folders and items. This data management system is integrated with JupyterHub~(\textbf{citeme}) and allows authenticated users to spawn Jupyter notebook servers with the direct access to data that is provided as a dynamically composed FUSE filesystem. Any Jupyter notebook created in that environment during an interactive session is safely stored back in the Girder instance, preserving the user's analysis workflow and increasing research reproducibility. In the future, we plan to have this notebook capability integrated directly with the catalog website.
